

\documentclass{resume} % Use the custom resume.cls style
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=black,
    filecolor=black,      
    urlcolor=black,
}
\urlstyle{same}
\usepackage[left=0.35in,top=0.25in,right=0.35in,bottom=0.25in]{geometry} % Document margins
\usepackage{fontawesome}
\name{Ishita Kumar}% Your name
\vspace{-1mm}



\address{
\\ \faLinkedinSquare \ \href{https://www.linkedin.com/in/ishitakumar96/} {ishitakumar96} 
\faGithub \href{https://github.com/ishita-kumar} \ {ishita-kumar}
\\ \faGlobe \href{http://ishita-kumar.github.io} \ {ishita-kumar.github.io} 
\\ \faPhone \ 812-369-3488 \\ \faEnvelope \ kumar.ishita@gmail.com} % Your address


\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\vspace{-5mm}
\begin{rSection}{Education}

{\bf Indiana University, Bloomington IN} \hfill {\em May 2021} 
\\ Masters of Science in Computer Science\hfill {\em 3.67/4.00} 
\\ Relewant Coursework: Software Engineering, Applied Algorithms \hfill 


\\{\bf NMIMS University, Mumbai India} \hfill {\em August 2018} 
\\ Bachelor of Technology in Computer Engineering.
\end{rSection}

\begin{rSection}{Technical Strengths}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Languages and Technologies \ & Java,Python, C++, C Flask, NodeJS, JavaScript, ReactJS, JQuery\\
Database \ & MySQL , MongoDB \\
Collaboration and Productivity Tools \ & JIRA, Slack, Git, Microsoft Teams, Asana \\
Professional Skills \ &  Agile Methodology, Scrum, Software Development Life Cycle \\

\end{tabular}

\end{rSection}

%--------------------------------------------------------------------------------

%----------------------------------------------------------------------------------------

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\vspace{-1mm}
\begin{rSection}{Work Experience}

\begin{rSubsection}{Software Developer,Tikona Infinet Pvt. Ltd}{Sep 18 - July 19}{}

    \item Implemented business projects using java, Servlets, JDBC, JSP , MYSql and Hibernate and NodeJS.
\item Enhanced the performance of the 3 Tier Mobile App, Customer Care Maintenance Portal and other server side components.
\item Wrote Scripts to automate the processes and developed multiple API's for extracting customers' billing information and payment deadlines,

\end{rSubsection}


\begin{rSubsection}{Intern-Software Developer, Competitive Exam Guide, India}{May 18 - July 18}{}{}
\item Designed a student registration portal using JavaScript, Bootstrap, JQuery and PHP to and automated the authentication and Hall pass generating process.
\item Upgraded the admin portal to view different demographics of students that registered onto their website  and enhance the customer interaction tactics. 
\end{rSubsection}

\begin{rSubsection}{Intern-Software Developer, TATA Power- Strategic Power and Engineering, India}{May 17 - July 17}{}{}
\item Evaluated technologies and tested tools under the performance team to collect system statistics such as CPU and Memory Usage.
\item Fixed a plethora of bugs with C++ administered in the Combat Management System Project used by the Indian Navy.

\end{rSubsection}




\end{rSection}
%    Projects And Seminars
%-----------------------------------------------------------------------------------------------
\vspace{-5mm}
\begin{rSection}{Projects}
{\bf Academic ProjectSmart Home Security System}:
A face Recognition System for Smart Homes Using the Raspberry Pi and Open-CV. Provided an accuracy of 94 percent in detecting different faces.\\
\vspace{-5mm}

\\{\bf E-Sanstha- Pragati Path}:
 A comprehensive literacy enhancement solution for rural areas with adaptive assessment and collaborative learning using Flask and JavaScript (Runner-up at the Newton-Bhabha Foundation Tech Challenge.\\
\vspace{-5mm}
\\{\bf Are You In}:
 A Website for browsing events and rentals in Bloomington. Search for events and venue, Wish list Events, chat with users, OAuth,Public Forums  using MongoDB, Express, ReactJS, NodeJS and the Agile Methodology for Development
\\{\bf Front End Development at Mankins Research, Bloomington IN }:
Worked across a team of 4 to develop a camp registration website using MongoDb, ReactJS, Express and NodeJS

\end{rSection}

%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------
\vspace{-5mm}
\begin{rSection}{Academic Achievements} 
 Published 3 research papers at different IEEE conferences and journals in  AI and Cloud Computing. 
\item Mentored,Instructed students aged 8-16 in the development of websites using Front-end technologies such as JavaScript, CSS, Bootstrap from July 2018 to September 2018 at Camp K-12 India 
\item Founder and Technical Director ,Project Evolve, NMIMS : Led a team of 400 Students and
Carried out various NGO visits, Debates, Sports Activities , Conferences and Technical Workshops.

\end{rSection}

\newpage



\end{document}
